### 2018-04-04 tex/paper.tex
small changes
Explain implementation of operations as transactions

\documentclass[
      acmsmall
    , screen
%    , authordraft
%    , anonymous
    , review=true
  ]{acmart}

% Metadata Information
\acmConference[ICFP]{International Conference on Functional Programming}{23--29 September 2018}{St.~Louis, Missouri, United States}
%\acmJournal{PACMPL}
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2010}
%\acmMonth{3}
%\copyrightyear{2009}
%\acmArticleSeq{9}

@@

>>>>

\documentclass[
      acmsmall
    , screen
%    , authordraft
%    , anonymous
%    , review=true
  ]{acmart}

% Metadata Information
%\acmConference[DRAFT]{Draft paper}
%\acmJournal{PACMPL}
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2010}
%\acmMonth{3}
%\copyrightyear{2009}
%\acmArticleSeq{9}

@@

Since the current version of Marlowe follows the `pull' model, a contract written in Marlowe could also be potentially
compiled to a contract written in Ethereum. This could be done in two ways, it could be compiled so that an Ethereum
contract represents a single instance of the contract (with a fixed set of participants), or alternatively it would be
possible to create a generic contract with an extra ``instantiate'' operation that sets-up' a new contract instance
with a given set of participants (represented by a set of public keys).

\paragraph{Transactions}

In principle, we can directly translate each operation in the model (i.e: cash commitment, payment claim, choice, or
redemption) into a separate transaction in the blockchain. In Ethereum model this would work in the same 
way that is simulated by Meadow: several operations can be issued in parallel and the blockchain subsystem will 
automatically apply them in some order and integrate them into the next block.

Another approach would be to use a UTXO model with continuations in which a UTXO represents a contract. In this model,
an operation would correspond to a transaction that spends a UTXO and creates (at least) a new UTXO that represents the 
contract after the operation.

Usually, in the UTXO model, it is necessary that a UTXO is in the blockchain in order for another transaction to be able 
to spend it. This could potentially limit the number of operations that can be applied in a single block to one, which 
would make infeasible the approach of using the same UTXO to represent several instances of the same contract (since it 
would not scale).

On the other hand, it would prevent non-determinism and, with it, it would remove the possibility of race-conditions. A 
change to the state of a contract before a transaction (and its corresponding operation) is accepted in the blockchain 
would invalidate the transaction and require the user to issue it again.

Even if we only allow one transaction per block, it would still be possible to combine several transactions off-chain 
and to issue a transaction that contains several operations. However, that would require an offline protocol 
independent from the blockchain and it would require participants to collaborate.
